On finiteness of structures produced deterministically by co-transcriptional folding

### 2018-11-13 ttt.tex
11/13 en

\usepackage[dvipdfmx]{color}

\usepackage[dvipdfmx]{graphicx}
\usepackage{tikz}
\usepackage{calc}
\usepackage{amsmath,amssymb}
\usetikzlibrary{automata}

@@

\begin{figure}
  \begin{center}
    \begin{tikzpicture}
      \draw[thick, rounded corners = 10pt]
      (-1,-1)--(7,-1)--(7,2)--(-1,2)-- cycle;

      \fill (0,0) circle[radius = 0.1];
      \fill (1.5,0) circle[radius = 0.1];
      \fill (3,0) circle[radius = 0.1];
      \fill (4.5,0) circle[radius = 0.1];
      \fill (6,0) circle[radius = 0.1];

@@

In this section, we prove that unary oritatami system can form infinitely at delay 1 and arity 1 deterministically moreover the infinite terminal which its oritatami system can yield is only zig-zag conformations shown in Fig\ref{TTT_zigzag}.

Let $\Xi$ be a deterministic oritatami system of delay 1 and arity 2. Assume its seed $\sigma$ consists of $n$ beads. Let us denote its transcript by $w = w_1 w_2 w_3 \cdots$ for some $w_1,w_2,w_3 \in \Sigma = \{e\}$. For $i \geq 0$ let $C_i$ be the unique elongation of $\sigma$ by $w[1..i]$ that is foldable by $\Xi$. Hence $C_0 = \sigma$.

Let us consider the stabilization of the $i$-th bead $a_i$ upon $C_{i-1}$. The bead cannot collaborate with any succeeding bead $w_{i+1},w_{i+2},\cdots$ at delay 1. There are just two ways to get stabilized at delay 1. One way is to be bound to another bead. The other way is through a $tunnel\ section$. A tunnel section consists of four beads that occupt four neighbors of a point(Fig.\ref{TTT_tunnel_intro}). Assume that four of the six neighbors of a point $p$ are occupied by beads $a_{j_1},a_{j_2},a_{j_3},a_{j_4}$ while the other two are not occupied. We call such beads as $p$ $inside\ of\ a\ tunnel$ and such beads as $p^\prime$ $entrance\ of\ a\ tunnel$ without a case that $p^\prime$ is inside of a tunnel. If the beads $a_{i-2}$ and $a_{i-1}$ are stabilized respectively at one of the two free neighbors and at $p$ one after another, then the next bead $a_i$ cannot help but be stabilized at the other free neighbor. In this way, $a_i$ can get stabilized without being bound.

@@

\begin{figure}
  \begin{center}
    \begin{tikzpicture}
      \fill (0:0) circle [radius=0.05];
      \fill (0:1.5) circle [radius=0.05];
      \fill (180:1.5) circle [radius=0.05];
      \node[above] at (0:1.5) { $p^\prime$ };
      \node[above] at (0:0) { $p$ };
      \node[above] at (180:1.5) { $p^\prime$ };

      \fill (60 : 1.5) circle [radius=0.1];
      \fill (-60 : 1.5) circle [radius=0.1];
      \fill (120 : 1.5) circle [radius=0.1];
      \fill (-120 : 1.5) circle [radius=0.1];
      \node[above] at (60 :1.5) { $a_{j_1}$ };
      \node[above] at (-60 :1.5) { $a_{j_2}$ };
      \node[above] at (120 :1.5) { $a_{j_3}$ };
      \node[above] at (-120 :1.5) { $a_{j_4}$ };

      \begin{scope}[shift=(0:5)]
        \fill (0:0) circle [radius=0.1];
        \fill (0:1.5) circle [radius=0.05];
        \fill (180:1.5) circle [radius=0.1];
        \node[above] at (180:1.5) { $a_{i-2}$ };
        \node[above] at (0:0) { $a_{i-1}$ };
        \draw[->] (180:1.4) -- (180:0.1);

        \fill (60 : 1.5) circle [radius=0.1];
        \fill (-60 : 1.5) circle [radius=0.1];
        \fill (120 : 1.5) circle [radius=0.1];
        \fill (-120 : 1.5) circle [radius=0.1];
        \node[above] at (60 :1.5) { $a_{j_1}$ };
        \node[above] at (-60 :1.5) { $a_{j_2}$ };
        \node[above] at (120 :1.5) { $a_{j_3}$ };
        \node[above] at (-120 :1.5) { $a_{j_4}$ };
      \end{scope}
      \begin{scope}[shift=(0:10)]
        \fill (0:0) circle [radius=0.1];
        \fill (0:1.5) circle [radius=0.1];
        \fill (180:1.5) circle [radius=0.1];
        \node[above] at (180:1.5) { $a_{i-2}$ };
        \node[above] at (0:0) { $a_{i-1}$ };
        \node[above] at (0:1.5) { $a_i$ };
        \draw[->] (180:1.4) -- (180:0.1);
        \draw[->] (0:0.1) -- (0:1.4);

        \fill (60 : 1.5) circle [radius=0.1];
        \fill (-60 : 1.5) circle [radius=0.1];
        \fill (120 : 1.5) circle [radius=0.1];
        \fill (-120 : 1.5) circle [radius=0.1];
        \node[above] at (60 :1.5) { $a_{j_1}$ };
        \node[above] at (-60 :1.5) { $a_{j_2}$ };
        \node[above] at (120 :1.5) { $a_{j_3}$ };
        \node[above] at (-120 :1.5) { $a_{j_4}$ };
      \end{scope}
    \end{tikzpicture} 
    \caption{Through a tunnel section}
    \label{TTT_tunnel_intro}
  \end{center}
\end{figure}

@@

      \begin{minipage}{0.3\hsize}
        \begin{tikzpicture}
          \draw[thick, rounded corners = 10pt]
          (0,0)--(4,0)--(4,4)--(0,4)-- cycle;

          \begin{scope}[xshift=2cm, yshift=2cm]
            \fill(0,0) circle [radius=0.05];
            \node[above] at (180:1.5) {$p^\prime$};
            \node[above] at (0:1.5) {$p^\prime$};

            \foreach \theta in {0,180}{
              \fill[transform canvas={shift=(\theta:1.5)}](0,0) circle [radius=0.05];
            }

            \foreach \theta in {60,-60,120,-120}{
              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
            }
          \end{scope}

          \node at (2,-0.5) {Tunnel A};
        \end{tikzpicture}
      \end{minipage}

      \begin{minipage}{0.3\hsize}
        \begin{tikzpicture}
          \draw[thick, rounded corners = 10pt]
          (0,0)--(4,0)--(4,4)--(0,4)-- cycle;

          \begin{scope}[xshift=2cm, yshift=2cm]
            \fill(0,0) circle [radius=0.05];
            \node[above] at (180:1.5) {$p^\prime$};
            \node[above] at (-60:1.5) {$p^\prime$};

            \foreach \theta in {-60,180}{
              \fill[transform canvas={shift=(\theta:1.5)}](0,0) circle [radius=0.05];
            }

            \foreach \theta in {0,60,120,-120}{
              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
            }
          \end{scope}

          \node at (2,-0.5) {Tunnel B};
        \end{tikzpicture}
      \end{minipage}

      \begin{minipage}{0.3\hsize}
        \begin{tikzpicture}
          \draw[thick, rounded corners = 10pt]
          (0,0)--(4,0)--(4,4)--(0,4)-- cycle;

          \begin{scope}[xshift=2cm, yshift=2cm]
            \fill(0,0) circle [radius=0.05];
            \node[above] at (180:1.5) {$p^\prime$};
            \node[above] at (-1200:1.5) {$p^\prime$};

            \foreach \theta in {-120,180}{
              \fill[transform canvas={shift=(\theta:1.5)}](0,0) circle [radius=0.05];
            }

            \foreach \theta in {0,60,-60,120}{
              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
            }
          \end{scope}

          \node at (2,-0.5) {Tunnel C};
        \end{tikzpicture}
      \end{minipage}

@@

      \begin{minipage}{0.45\hsize}
        \begin{tikzpicture}
          \draw[thick, rounded corners = 10pt]
          (0,0)--(2.5,0)--(2.5,4)--(0,4)-- cycle;

          \begin{scope}[xshift=2cm, yshift=2cm]
            \fill(0,0) circle [radius=0.1];
            \node[above] at (180:1.5) {$p^\prime$};

            \fill[transform canvas={shift=(180:1.5)}](0,0) circle [radius=0.1];

            \foreach \theta in {120,-120}{
              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
            }

            \draw[->] (-1.4,0) -- (-0.1,0);
          \end{scope}

          \node at (1.25,-0.5) {Tunnel A,B};
        \end{tikzpicture}
      \end{minipage}

      \begin{minipage}{0.45\hsize}
        \begin{tikzpicture}
          \draw[thick, rounded corners = 10pt]
          (0,0)--(2.5,0)--(2.5,4)--(0,4)-- cycle;

          \begin{scope}[xshift=2cm, yshift=2cm]
            \fill(0,0) circle [radius=0.1];
            \node[above] at (180:1.5) {$p^\prime$};

            \draw[transform canvas={shift=(-120:1.5)}](0,0) circle [radius=0.1];
            \fill[transform canvas={shift=(180:1.5)}](0,0) circle [radius=0.1];

            \foreach \theta in {120}{
              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
            }

            \draw[->] (-1.4,0) -- (-0.1,0);
          \end{scope}

          \node at (1.25,-0.5) {Tunnel C};
        \end{tikzpicture}
      \end{minipage}

@@

    \end{tikzpicture}
    \caption{Tunnel A,Bにおけるbondの増加量}
    \label{TTT_position2}
  \end{center}
\end{figure}

\begin{figure}[h]
  \begin{center}
    \begin{tikzpicture}
      \node at (0,4)   [rectangle, draw,rounded corners] (outside1) {Otherwise};
      \node at (4.5,4) [rectangle, draw,rounded corners] (enter1)   {Entrance of a tunnel};
      \node at (8,4)   [rectangle, draw, rounded corners] (inside1) {Inside of a tunnel C};
      \node at (11,4)  [rectangle, draw, rounded corners] (exit1)   {Inside of a tunnel A or B};
      \draw[->] (outside1)--(enter1);
      \draw[->] (enter1)  --(inside1);
      \draw[->] (inside1) --(exit1);

      \node at (0,3)   [rectangle, draw,rounded corners] (outside2) {Inside of a tunnel};
      \node at (4.5,3) [rectangle, draw,rounded corners] (enter2)   {Entrance of a tunnel};
      \node at (8,3)   [rectangle, draw, rounded corners] (inside2) {Inside of a tunnel C};
      \node at (11,3)  [rectangle, draw, rounded corners] (exit2)   {Inside of a tunnel A or B};     
      \draw[->] (outside2)--(enter2);
      \draw[->] (enter2)  --(inside2);
      \draw[->] (inside2) --(exit2);

      \node at (0,1)   [rectangle, draw,rounded corners] (outside3) {トンネルから離れている};
      \node at (4.5,1) [rectangle, draw,rounded corners] (enter3)   {トンネルの入り口};
      \node at (8,1)   [rectangle, draw, rounded corners] (inside3) {トンネルC};
      \node at (11,1)  [rectangle, draw, rounded corners] (exit3)   {トンネルの外};     
      \draw[->] (outside3)--(enter3);
      \draw[->] (enter3)  --(inside3);
      \draw[->] (inside3) --(exit3);

      \node at (0,0)   [rectangle, draw,rounded corners] (outside4) {トンネルの中};
      \node at (4.5,0) [rectangle, draw,rounded corners] (enter4)   {トンネルの入り口};
      \node at (8,0)   [rectangle, draw, rounded corners] (inside4) {トンネルC};
      \node at (11,0)  [rectangle, draw, rounded corners] (exit4)   {トンネルの外};     
      \draw[->] (outside4)--(enter4);
      \draw[->] (enter4)  --(inside4);
      \draw[->] (inside4) --(exit4);
    \end{tikzpicture}
    \caption{Tunnel Cの場合分け}
    \label{TTT_tunnelC_graph}
  \end{center}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
    \begin{tabular}{ccc}

      \begin{minipage}{0.3\hsize}
        \begin{tikzpicture}
          \draw[thick, rounded corners = 10pt]
          (0,0)--(4,0)--(4,4)--(0,4)-- cycle;

@@

            \foreach \theta in {0}{
              \draw[transform canvas={shift=(\theta:1.5)}](0,0) circle [radius=0.1];
            }

            \foreach \theta in {60,-60,180}{
              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
            }

            \foreach \theta in {120,-120}{
              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1) rectangle (0.1,0.1);
            }

            \draw[->] (180:1.4)--(180:0.1);
            \draw[->] (0:0.1)--(0:1.4);

            \node[transform canvas={shift=(60:1.5)},right] {A};
            \node[transform canvas={shift=(-60:1.5)},right] {B};

            \node[transform canvas={shift=(120:1.5)},left] {c};
            \node[transform canvas={shift=(-120:1.5)},left] {d};
          \end{scope}

@@

      \begin{minipage}{0.3\hsize}
        \begin{tikzpicture}
          \draw[thick, rounded corners = 10pt]
          (0,0)--(4,0)--(4,4)--(0,4)-- cycle;

@@

            \foreach \theta in {0}{
              \draw[transform canvas={shift=(\theta:1.5)}](0,0) circle [radius=0.1];
            }

            \foreach \theta in {60,-60,120}{
              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
            }

            \foreach \theta in {180,-120}{
              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1) rectangle (0.1,0.1);
            }

            \draw[->] (120:1.4)--(120:0.1);
            \draw[->] (0:0.1)--(0:1.4);

            \node[transform canvas={shift=(60:1.5)},right] {A};
            \node[transform canvas={shift=(-60:1.5)},right] {B};
            \node[transform canvas={shift=(120:1.5)},left] {P};

            \node[transform canvas={shift=(180:1.5)},left] {c};
            \node[transform canvas={shift=(-120:1.5)},left] {d};
          \end{scope}

@@

            \foreach \theta in {0}{
              \draw[transform canvas={shift=(\theta:1.5)}](0,0) circle [radius=0.1];
            }

            \foreach \theta in {60,-60}{
              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
            }

            \foreach \theta in {180,-120,120}{
              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1) rectangle (0.1,0.1);
            }

            \draw[->] (60:1.4)--(60:0.1);
            \draw[->] (0:0.1)--(0:1.4);

            \node[transform canvas={shift=(-60:1.5)},right] {A};
            \node[transform canvas={shift=(60:1.5)},right] {P};

            \node[transform canvas={shift=(120:1.5)},left] {c};
            \node[transform canvas={shift=(180:1.5)},left] {d};
            \node[transform canvas={shift=(-120:1.5)},left] {e};
            \node[transform canvas={shift=(0:1.5)},below] {n};
          \end{scope}

@@

      \begin{minipage}{0.48\hsize}
        \begin{tikzpicture}
          \draw[thick, rounded corners = 10pt]
          (0,0)--(4,0)--(4,4)--(0,4)-- cycle;

            \foreach \theta in {120,-120,180}{
              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
            }

            \foreach \theta in {0,60,-60}{
              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1) rectangle (0.1,0.1);
            }

            \draw[->] (180:1.4)--(180:0.1);

            \node[transform canvas={shift=(120:1.5)},right] {A};
            \node[transform canvas={shift=(-120:1.5)},right] {B};
            \node[transform canvas={shift=(180:1.5)},left] {P};

            \node[transform canvas={shift=(60:1.5)},left] {c};
            \node[transform canvas={shift=(-60:1.5)},left] {d};
          \end{scope}

          \node at (2,-0.5) {Point $c$ and $d$ are free};
        \end{tikzpicture}
      \end{minipage}

      \begin{minipage}{0.48\hsize}
        \begin{tikzpicture}
          \draw[thick, rounded corners = 10pt]
          (0,0)--(4,0)--(4,4)--(0,4)-- cycle;

            \foreach \theta in {120,-120,180,60}{
              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
            }

            \foreach \theta in {0,-60}{
              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1) rectangle (0.1,0.1);
            }

            \draw[->] (180:1.4)--(180:0.1);

            \node[transform canvas={shift=(120:1.5)},right] {A};
            \node[transform canvas={shift=(-120:1.5)},right] {B};
            \node[transform canvas={shift=(180:1.5)},left] {P};

>>>>

\usepackage{tikz}
\usepackage{calc}
\usepackage{amsmath,amssymb}
\usetikzlibrary{automata}

@@

\begin{figure}
  \begin{center}
    \begin{tikzpicture}
      \fill (0,0) circle[radius = 0.1];
      \fill (1.5,0) circle[radius = 0.1];
      \fill (3,0) circle[radius = 0.1];
      \fill (4.5,0) circle[radius = 0.1];
      \fill (6,0) circle[radius = 0.1];

@@

In this section, we prove that unary oritatami system can form infinitely at delay 1 and arity 2 deterministically and moreover that the only infinite conformations which its oritatami system can yield is only the zig-zag conformation shown in Fig.\ref{TTT_zigzag}.

Let $\Xi$ be a deterministic oritatami system of delay 1 and arity 2. Assume its seed $\sigma$ consists of $n$ beads.
%Let us denote its transcript by $w = w_1 w_2 w_3 \cdots$ for some $w_1,w_2,w_3 \in \Sigma = \{e\}$.
For $i \geq 0$ let $C_i$ be the unique elongation of $\sigma$ by $w[1..i]$ that is foldable by $\Xi$. Hence $C_0 = \sigma$.

Let us consider the stabilization of the $i$-th bead $a_i$ upon $C_{i-1}$. The bead cannot collaborate with any succeeding bead $w[i+1],w[i+2],\cdots$ at delay 1. There are just two ways to get stabilized at delay 1. One way is to be bound to another bead. The other way is through a $tunnel\ section$. A tunnel section consists of four beads that occupy four neighbors of a point (Fig.\ref{TTT_tunnel_intro}). Assume that four of the six neighbors of a point $p$ are occupied by beads $a_{j_1},a_{j_2},a_{j_3},a_{j_4}$ while the other two are free. We call such beads as $p$ $inside\ of\ a\ tunnel$ and such beads as $p^\prime$ $entrance\ of\ a\ tunnel$ without a case that $p^\prime$ is inside of a tunnel. If the beads $w[i-2]$ and $w[i-1]$ are stabilized respectively at one of the two free neighbors and at $p$ one after another, then the next bead $w[i]$ cannot help but be stabilized at the other free neighbor. In this way, $w[i]$ can get stabilized without being bound.

@@

\begin{figure}
  \begin{center}
    \begin{tikzpicture}
      \fill (0:0) circle [radius=0.05];
      \fill (0:1.2) circle [radius=0.05];
      \fill (180:1.2) circle [radius=0.05];
      \node[above] at (0:1.2) { $p^\prime$ };
      \node[above] at (0:0) { $p$ };
      \node[above] at (180:1.2) { $p^\prime$ };

      \fill (60 : 1.2) circle [radius=0.1];
      \fill (-60 : 1.2) circle [radius=0.1];
      \fill (120 : 1.2) circle [radius=0.1];
      \fill (-120 : 1.2) circle [radius=0.1];
      \node[above] at (60 :1.2) { $a_{j_1}$ };
      \node[above] at (-60 :1.2) { $a_{j_2}$ };
      \node[above] at (120 :1.2) { $a_{j_3}$ };
      \node[above] at (-120 :1.2) { $a_{j_4}$ };

      \begin{scope}[shift=(0:5)]
        \fill (0:0) circle [radius=0.1];
        \fill (0:1.2) circle [radius=0.05];
        \fill (180:1.2) circle [radius=0.1];
        \node[above] at (180:1.2) { $a_{i-2}$ };
        \node[above] at (0:0) { $a_{i-1}$ };
        \draw[->] (180:1.1) -- (180:0.1);

        \fill (60 : 1.2) circle [radius=0.1];
        \fill (-60 : 1.2) circle [radius=0.1];
        \fill (120 : 1.2) circle [radius=0.1];
        \fill (-120 : 1.2) circle [radius=0.1];
        \node[above] at (60 :1.2) { $a_{j_1}$ };
        \node[above] at (-60 :1.2) { $a_{j_2}$ };
        \node[above] at (120 :1.2) { $a_{j_3}$ };
        \node[above] at (-120 :1.2) { $a_{j_4}$ };
      \end{scope}
      \begin{scope}[shift=(0:10)]
        \fill (0:0) circle [radius=0.1];
        \fill (0:1.2) circle [radius=0.1];
        \fill (180:1.2) circle [radius=0.1];
        \node[above] at (180:1.2) { $a_{i-2}$ };
        \node[above] at (0:0) { $a_{i-1}$ };
        \node[above] at (0:1.2) { $a_i$ };
        \draw[->] (180:1.1) -- (180:0.1);
        \draw[->] (0:0.1) -- (0:1.1);

        \fill (60 : 1.2) circle [radius=0.1];
        \fill (-60 : 1.2) circle [radius=0.1];
        \fill (120 : 1.2) circle [radius=0.1];
        \fill (-120 : 1.2) circle [radius=0.1];
        \node[above] at (60 :1.2) { $a_{j_1}$ };
        \node[above] at (-60 :1.2) { $a_{j_2}$ };
        \node[above] at (120 :1.2) { $a_{j_3}$ };
        \node[above] at (-120 :1.2) { $a_{j_4}$ };
      \end{scope}
    \end{tikzpicture} 
    \caption{Through a tunnel section}
    \label{TTT_tunnel_intro}
  \end{center}
\end{figure}

@@

      \begin{minipage}{0.3\hsize}
        \begin{tikzpicture}
          \begin{scope}[xshift=2cm, yshift=2cm]
            \fill(0,0) circle [radius=0.05];
            \node[above] at (180:1.2) {$p^\prime$};
            \node[above] at (0:1.2) {$p^\prime$};

            \foreach \theta in {0,180}{
              \fill[transform canvas={shift=(\theta:1.2)}](0,0) circle [radius=0.05];
            }

            \foreach \theta in {60,-60,120,-120}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
            }
          \end{scope}

          \node at (2,0) {Tunnel A};
        \end{tikzpicture}
      \end{minipage}

      \begin{minipage}{0.3\hsize}
        \begin{tikzpicture}

          \begin{scope}[xshift=2cm, yshift=2cm]
            \fill(0,0) circle [radius=0.05];
            \node[above] at (180:1.2) {$p^\prime$};
            \node[above] at (-60:1.2) {$p^\prime$};

            \foreach \theta in {-60,180}{
              \fill[transform canvas={shift=(\theta:1.2)}](0,0) circle [radius=0.05];
            }

            \foreach \theta in {0,60,120,-120}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
            }
          \end{scope}

          \node at (2,0) {Tunnel B};
        \end{tikzpicture}
      \end{minipage}

      \begin{minipage}{0.3\hsize}
        \begin{tikzpicture}

          \begin{scope}[xshift=2cm, yshift=2cm]
            \fill(0,0) circle [radius=0.05];
            \node[above] at (180:1.2) {$p^\prime$};
            \node[above] at (-1200:1.2) {$p^\prime$};

            \foreach \theta in {-120,180}{
              \fill[transform canvas={shift=(\theta:1.2)}](0,0) circle [radius=0.05];
            }

            \foreach \theta in {0,60,-60,120}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
            }
          \end{scope}

          \node at (2,0) {Tunnel C};
        \end{tikzpicture}
      \end{minipage}

@@

\begin{figure}
  \begin{center}
    \begin{tabular}{lr}

      \begin{minipage}{0.2\hsize}
        \begin{tikzpicture}

          \begin{scope}[xshift=1cm, yshift=2cm]
            \fill(0,0) circle [radius=0.1];
            \node[above] at (180:1.2) {$p^\prime$};

            \fill[transform canvas={shift=(180:1.2)}](0,0) circle [radius=0.1];

            \foreach \theta in {120,-120}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
            }

            \draw[->] (-1.1,0) -- (-0.1,0);
          \end{scope}

          \node at (0.25,0) {Tunnel A,B};
        \end{tikzpicture}
      \end{minipage}

      \begin{minipage}{0.2\hsize}
        \begin{tikzpicture}

          \begin{scope}[xshift=1cm, yshift=2cm]
            \fill(0,0) circle [radius=0.1];
            \node[above] at (180:1.2) {$p^\prime$};

            \draw[transform canvas={shift=(-120:1.2)}](0,0) circle [radius=0.1];
            \fill[transform canvas={shift=(180:1.2)}](0,0) circle [radius=0.1];

            \foreach \theta in {120}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
            }

            \draw[->] (-1.1,0) -- (-0.1,0);
          \end{scope}

          \node at (0.25,0) {Tunnel C};
        \end{tikzpicture}
      \end{minipage}

@@

    \end{tikzpicture}
    \caption{Increment on Tunnel A,B}
    \label{TTT_position2}
  \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \begin{tikzpicture}
      \node at (0,4)   [rectangle, draw,rounded corners] (outside1) {Outside of tunnels};
      \node at (3.5,4) [rectangle, draw,rounded corners] (enter1)   {Entrance of a tunnel};
      \node at (7,4)   [rectangle, draw, rounded corners] (inside1) {Inside of a tunnel C};
      \node at (11,4)  [rectangle, draw, rounded corners] (exit1)   {Inside of a tunnel A or B};
      \draw[->] (outside1)--(enter1);
      \draw[->] (enter1)  --(inside1);
      \draw[->] (inside1) --(exit1);

      \node at (0,3)   [rectangle, draw,rounded corners] (outside2) {Inside of a tunnel};
      \node at (3.5,3) [rectangle, draw,rounded corners] (enter2)   {Entrance of a tunnel};
      \node at (7,3)   [rectangle, draw, rounded corners] (inside2) {Inside of a tunnel C};
      \node at (11,3)  [rectangle, draw, rounded corners] (exit2)   {Inside of a tunnel A or B};     
      \draw[->] (outside2)--(enter2);
      \draw[->] (enter2)  --(inside2);
      \draw[->] (inside2) --(exit2);

      \node at (0,1)   [rectangle, draw,rounded corners] (outside3) {Outside of tunnels};
      \node at (3.5,1) [rectangle, draw,rounded corners] (enter3)   {Entrance of a tunnel};
      \node at (7,1)   [rectangle, draw, rounded corners] (inside3) {Inside of a tunnel C};
      \node at (11,1)  [rectangle, draw, rounded corners] (exit3)   {Outside of tunnels};     
      \draw[->] (outside3)--(enter3);
      \draw[->] (enter3)  --(inside3);
      \draw[->] (inside3) --(exit3);

      \node at (0,0)   [rectangle, draw,rounded corners] (outside4) {Inside of atunnel};
      \node at (3.5,0) [rectangle, draw,rounded corners] (enter4)   {Entrance of a tunnel};
      \node at (7,0)   [rectangle, draw, rounded corners] (inside4) {Inside of a tunnel C};
      \node at (11,0)  [rectangle, draw, rounded corners] (exit4)   {Outside of tunnels};     
      \draw[->] (outside4)--(enter4);
      \draw[->] (enter4)  --(inside4);
      \draw[->] (inside4) --(exit4);
    \end{tikzpicture}
    \caption{Case of Tunnel C}
    \label{TTT_tunnelC_graph}
  \end{center}
\end{figure}

@@

      \begin{minipage}{0.3\hsize}
        \begin{tikzpicture}

@@

            \foreach \theta in {0}{
              \draw[transform canvas={shift=(\theta:1.2)}](0,0) circle [radius=0.1];
            }

            \foreach \theta in {60,-60,180}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
            }

            \foreach \theta in {120,-120}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
            }

            \draw[->] (180:1.1)--(180:0.1);
            \draw[->] (0:0.1)--(0:1.1);

            \node[transform canvas={shift=(60:1.2)},right] {A};
            \node[transform canvas={shift=(-60:1.2)},right] {B};

            \node[transform canvas={shift=(120:1.2)},left] {c};
            \node[transform canvas={shift=(-120:1.2)},left] {d};
          \end{scope}

@@

      \begin{minipage}{0.3\hsize}
        \begin{tikzpicture}

@@

            \foreach \theta in {0}{
              \draw[transform canvas={shift=(\theta:1.2)}](0,0) circle [radius=0.1];
            }

            \foreach \theta in {60,-60,120}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
            }

            \foreach \theta in {180,-120}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
            }

            \draw[->] (120:1.1)--(120:0.1);
            \draw[->] (0:0.1)--(0:1.1);

            \node[transform canvas={shift=(60:1.2)},right] {A};
            \node[transform canvas={shift=(-60:1.2)},right] {B};
            \node[transform canvas={shift=(120:1.2)},left] {P};

            \node[transform canvas={shift=(180:1.2)},left] {c};
            \node[transform canvas={shift=(-120:1.2)},left] {d};
          \end{scope}

@@

            \foreach \theta in {0}{
              \draw[transform canvas={shift=(\theta:1.2)}](0,0) circle [radius=0.1];
            }

            \foreach \theta in {60,-60}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
            }

            \foreach \theta in {180,-120,120}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
            }

            \draw[->] (60:1.1)--(60:0.1);
            \draw[->] (0:0.1)--(0:1.1);

            \node[transform canvas={shift=(-60:1.2)},right] {A};
            \node[transform canvas={shift=(60:1.2)},right] {P};

            \node[transform canvas={shift=(120:1.2)},left] {c};
            \node[transform canvas={shift=(180:1.2)},left] {d};
            \node[transform canvas={shift=(-120:1.2)},left] {e};
            \node[transform canvas={shift=(0:1.2)},below] {n};
          \end{scope}

@@

\begin{figure}
  \centering
    \begin{tabular}{cc}

      \begin{minipage}{0.48\linewidth}
      \centering
        \begin{tikzpicture}

            \fill(0,0) circle [radius=0.1];
            \node[above] at (0,0) {$p^\prime$};

            \foreach \theta in {120,-120,180}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
            }

            \foreach \theta in {0,60,-60}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
            }

            \draw[->] (180:1.1)--(180:0.1);

            \node[transform canvas={shift=(120:1.2)},right] {A};
            \node[transform canvas={shift=(-120:1.2)},right] {B};
            \node[transform canvas={shift=(180:1.2)},left] {P};

            \node[transform canvas={shift=(60:1.2)},left] {c};
            \node[transform canvas={shift=(-60:1.2)},left] {d};

          \node at (0,-2) {Point $c$ and $d$ are free};
        \end{tikzpicture}
      \end{minipage}

      \begin{minipage}{0.48\linewidth}
      \centering
        \begin{tikzpicture}

            \fill(0,0) circle [radius=0.1];
            \node[above] at (0,0) {$p^\prime$};

            \foreach \theta in {120,-120,180,60}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
            }

            \foreach \theta in {0,-60}{
              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
            }

            \draw[->] (180:1.1)--(180:0.1);

            \node[transform canvas={shift=(120:1.2)},right] {A};
            \node[transform canvas={shift=(-120:1.2)},right] {B};
            \node[transform canvas={shift=(180:1.2)},left] {P};

            \node[transform canvas={shift=(-60:1.2)},right] {d};
            \node[transform canvas={shift=(60:1.2)},right] {c};
            \node[transform canvas={shift=(0:1.2)},right] {e};

          \node at (0,-2) {Point $c$ is occupied};
        \end{tikzpicture}
      \end{minipage}
